%  LaTeX template for abstract submission of contributed talks for MCM 2021 (thanks to MCM 2019 and its organizers)




\speaker{Jonathan}{Wenger}%
%  (put no space here)
% Title of the talk, capitalized.
\title{Probabilistic Numerical Methods -- An Algorithmic Perspective.}

% For each author, give the first name, family name, affiliation, and email.
% Ideally, the affiliation and email should fit on a single line.  
% No need to put the full snail mailing address.  

\author{Jonathan}{Wenger}{Universit\"at Tübingen}{jonathan.wenger@uni-tuebingen.de}

% Type your abstract here.
\abstract{
\emph{Probabilistic numerical methods} (PNMs) \cite{Hennig2015a, Oates2019,Cockayne2019a} aim to explicitly represent uncertainty resulting from limited computational resources and stochastic input in numerical computation. This emerging paradigm treats a numerical problem as one of statistical inference instead. It holds the promise to improve upon classic methods in areas where adaptivity is needed, related problems are solved repeatedly, stochasticity plays a role and solutions are not unique. However, one key barrier to the wider adoption of such methods is the lack of probabilistic numerics software. 

In this talk, we demonstrate how the theoretical formulation of PNMs can be translated into an algorithmic framework and introduce \textsc{ProbNum} -- a software stack for probabilistic numerics.
It enables the composition of problem-specific PNMs and paves the way for consistent propagation of uncertainty through the entirety of a computational pipeline.
	
	
%  If you have references, put them here in a format like below. 
%  This can be obtained using BiBTeX with the bib style plain.bst. 
%  Note that this must be placed inside the abstract.
\begin{thebibliography}{41}
    \providecommand{\natexlab}[1]{#1}
    
    \bibitem{Hennig2015a}
    P.~Hennig, M.~A. Osborne, and M.~Girolami.
    \newblock Probabilistic numerics and uncertainty in computations.
    \newblock \emph{Proc. A.}, 471\penalty0 (2179):\penalty0 20150142, 17, 2015.
    
    \bibitem{Oates2019}
    C.~J. Oates and T.~J. Sullivan.
    \newblock A modern retrospective on probabilistic numerics.
    \newblock \emph{Stat. Comput.}, 29\penalty0 (6):\penalty0 1335--1351, 2019.
    
    \bibitem{Cockayne2019a}
    J.~Cockayne, C.~J. Oates, T.~J. Sullivan, and M.~Girolami.
    \newblock Bayesian probabilistic numerical methods.
    \newblock \emph{SIAM Rev.}, 61\penalty0 (4):\penalty0 756--789,
      2019{\natexlab{a}}.


\end{thebibliography}
}  % End of abstract.


